---
title: "Mtcars prediction"
author: "Aravind"
date: "April 18, 2018"
output: ioslides_presentation
runtime: shiny
---



## Introduction

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).

A data frame with 32 observations on 11 variables.

1.   mpg	 Miles/(US) gallon
2.	 cyl	 Number of cylinders
3.   disp	 Displacement (cu.in.)
4.	 hp	 Gross horsepower
5.	 drat	 Rear axle ratio
6.	 wt	 Weight (1000 lbs)
7.	 qsec	 1/4 mile time
8.	 vs	 V/S
9.	 am	 Transmission (0 = automatic, 1 = manual)
10.	 gear	 Number of forward gears
11.	 carb	 Number of carburetors

## ui.R code

```{r, echo=TRUE, eval=FALSE}
library(shiny)
shinyUI(fluidPage(
      titlePanel("Predict horsepower from no of cylinders and miles per gallon"),
    sidebarLayout(
    sidebarPanel(
       sliderInput("SliderMpg","Miles per Gallon:", min = 10,max = 34,value = 30),
       sliderInput("SliderCyl","No of Cylinders:", min = 4,max = 8,2),
       checkboxInput("showModel1","Show/Hide Model 1", value = T),
       checkboxInput("showModel2","Show/Hide Model 1", value = T)
    ),
        mainPanel(
       plotOutput("plot1"),
       h3("Predicted hp from model 1:"),
       textOutput("pred1"),
       h3("Predicted hp from model 2:"),
       textOutput("pred2")
    )
  )
))

```

## server.R

```{r, echo=TRUE,eval=FALSE}
library(shiny)
shinyServer(function(input, output) {
   model1 <- lm(hp~mpg, data = mtcars)
   model2 <- lm(hp~mpg+cyl,data = mtcars)
   model1pred <-reactive({
     mpgInput <- input$SliderMpg
     predict(model1, newdata = data.frame(mpg = mpgInput))
   })
    model2pred <- reactive({
     mpgInput <- input$SliderMpg
     cylInput <- input$SliderCyl
     predict(model2, newdata = 
               data.frame(mpg = mpgInput,cyl = cylInput))
   })
  output$plot1 <- renderPlot({
    mpgInput <- input$SliderMpg
    cylInput <- input$SliderCyl
    plot(mtcars$mpg, mtcars$hp, xlab = "Miles per Gallon",
         ylab = "Horsepower", bty = "n", pch =16,xlim = c(10,35), ylim = c(50,350))
    if(input$showModel1){
      abline(model1, col = "red", lwd = 2)
    }
    if(input$showModel2){
      model2lines <- predict(model2, newdata= data.frame(mpg = 10:35, cyl = cylInput))
      lines(10:35, model2lines, col = "blue", lwd = 2)
   }
    legend(25,250,c("Model 1 Prediction", "Model 2 Prediction"), pch =16,
           col = c("red","blue"), bty = "n", cex = 1.2)
    points(mpgInput, model1pred(), col = "blue", pch = 16, cex =2)
  })
 output$pred1 <- renderText({
  model1pred()
  })
output$pred2 <- renderText({
  model2pred()
})
})
```


```{r,include=FALSE}
library(shiny)
shinyUI(fluidPage(
      titlePanel("Predict horsepower from no of cylinders and miles per gallon"),
    sidebarLayout(
    sidebarPanel(
       sliderInput("SliderMpg","Miles per Gallon:", min = 10,max = 34,value = 30),
       sliderInput("SliderCyl","No of Cylinders:", min = 4,max = 8,2),
       checkboxInput("showModel1","Show/Hide Model 1", value = T),
       checkboxInput("showModel2","Show/Hide Model 1", value = T)
    ),
        mainPanel(
       plotOutput("plot1"),
       h3("Predicted hp from model 1:"),
       textOutput("pred1"),
       h3("Predicted hp from model 2:"),
       textOutput("pred2")
    )
  )
))
shinyServer(function(input, output) {
   model1 <- lm(hp~mpg, data = mtcars)
   model2 <- lm(hp~mpg+cyl,data = mtcars)
   model1pred <-reactive({
     mpgInput <- input$SliderMpg
     predict(model1, newdata = data.frame(mpg = mpgInput))
   })
    model2pred <- reactive({
     mpgInput <- input$SliderMpg
     cylInput <- input$SliderCyl
     predict(model2, newdata = 
               data.frame(mpg = mpgInput,cyl = cylInput))
   })
  output$plot1 <- renderPlot({
    mpgInput <- input$SliderMpg
    cylInput <- input$SliderCyl
    plot(mtcars$mpg, mtcars$hp, xlab = "Miles per Gallon",
         ylab = "Horsepower", bty = "n", pch =16,xlim = c(10,35), ylim = c(50,350))
    if(input$showModel1){
      abline(model1, col = "red", lwd = 2)
    }
    if(input$showModel2){
      model2lines <- predict(model2, newdata= data.frame(mpg = 10:35, cyl = cylInput))
      lines(10:35, model2lines, col = "blue", lwd = 2)
   }
    legend(25,250,c("Model 1 Prediction", "Model 2 Prediction"), pch =16,
           col = c("red","blue"), bty = "n", cex = 1.2)
    points(mpgInput, model1pred(), col = "blue", pch = 16, cex =2)
  })
 output$pred1 <- renderText({
  model1pred()
  })
output$pred2 <- renderText({
  model2pred()
})
})
```


## Interactive Plot

```{r, echo=FALSE}
library(shiny)
shinyUI(fluidPage(
      titlePanel("Predict horsepower from no of cylinders and miles per gallon"),
    sidebarLayout(
    sidebarPanel(
       sliderInput("SliderMpg","Miles per Gallon:", min = 10,max = 34,value = 30),
       sliderInput("SliderCyl","No of Cylinders:", min = 4,max = 8,2),
       checkboxInput("showModel1","Show/Hide Model 1", value = T),
       checkboxInput("showModel2","Show/Hide Model 1", value = T)
    ),
        mainPanel(
       plotOutput("plot1"),
       h3("Predicted hp from model 1:"),
       textOutput("pred1"),
       h3("Predicted hp from model 2:"),
       textOutput("pred2")
    )
  )
))
shinyServer(function(input, output) {
   model1 <- lm(hp~mpg, data = mtcars)
   model2 <- lm(hp~mpg+cyl,data = mtcars)
   model1pred <-reactive({
     mpgInput <- input$SliderMpg
     predict(model1, newdata = data.frame(mpg = mpgInput))
   })
    model2pred <- reactive({
     mpgInput <- input$SliderMpg
     cylInput <- input$SliderCyl
     predict(model2, newdata = 
               data.frame(mpg = mpgInput,cyl = cylInput))
   })
  output$plot1 <- renderPlot({
    mpgInput <- input$SliderMpg
    cylInput <- input$SliderCyl
    plot(mtcars$mpg, mtcars$hp, xlab = "Miles per Gallon",
         ylab = "Horsepower", bty = "n", pch =16,xlim = c(10,35), ylim = c(50,350))
    if(input$showModel1){
      abline(model1, col = "red", lwd = 2)
    }
    if(input$showModel2){
      model2lines <- predict(model2, newdata= data.frame(mpg = 10:35, cyl = cylInput))
      lines(10:35, model2lines, col = "blue", lwd = 2)
   }
    legend(25,250,c("Model 1 Prediction", "Model 2 Prediction"), pch =16,
           col = c("red","blue"), bty = "n", cex = 1.2)
    points(mpgInput, model1pred(), col = "blue", pch = 16, cex =2)
  })
 output$pred1 <- renderText({
  model1pred()
  })
output$pred2 <- renderText({
  model2pred()
})
})
```



